ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-08 rebuttal.tex

    We have modified the text on \textbf{page 2} to clarify this point, including describing the lack of human
    readability as a formatting issue (but one that is inherent to XML), rather than a technical
    issue.
    %
\end{response}

\begin{reviewer}
    %
    I suggest adding to following block to this para:

    ``The original PrIMe was on an Amazon cloud server. Recently it was shifted to the computer
    center of DLR Stuttgart. At the new location it is called ``PrIMe 2.0''
    [\url{https://prime.cki-know.org/}]. This is identical to the original PrIMe apart from
    technical changes due to the different computation background. Professor Frenklach plans to
    develop further PrIMe (using name PrIMe 3.0) and this version will be availabe at
    [\url{http://primekinetics.org/}].''
    %
\end{reviewer}

\begin{response}
    %
    We do not think that the technical details of the implementation of the original PrIMe system
    (including a soon-to-be outdated URL for PrIMe 2.0) are relevant to this work, so we have not
    included them. In addition, we cannot know the plans of Prof.~Frenklach, and we do not feel it
    would be appropriate to comment on them in our manuscript. As such, we have not added these
    suggestions to the paper. However, we have moved the URL for PrIMe 3.0 from a footnote into the
    course of the main text on \textbf{page 2}.
    %
\end{response}

### 2017-10-08 pyked.tex
Move PrIMe URL from footnote to text

The combustion community has not yet widely adopted a standard format for
experimental data, but some researchers and groups have proposed solutions to
this problem. Most notably, Frenklach developed the PrIMe (\textbf{Pr}ocess
\textbf{I}nformatics \textbf{M}od\textbf{e}l) data
format~\autocite{Frenklach:2007bm,You:2011hy} and an associated online database,
the PrIMe Data Warehouse.\footnote{\url{http://primekinetics.org}}
PrIMe files encode fundamental
combustion experimental data, along with kinetic models and calculated
quantities, using the eXtensible Markup Language (XML) standard.

PrIMe~\autocite{Frenklach:2007bm,You:2011hy} (available at \url{http://primekinetics.org/})
has a number of features that make
it a strong standardization format, but it suffers from several flaws that
prevent wide adoption. First, the PrIMe standard does not require or support all
the information needed to simulate an experiment, including a machine-readable
definition of ignition or a standard way to express detailed facility-specific
effects necessary to properly simulate certain experiments. Second, PrIMe uses
internal identifiers for bibliographic references and
species\slash reactions, rather than standard identifiers (e.g., DOIs for
scholarly products, InCHI or SMILES for species). This limits the usability of PrIMe files outside
the PrIMe ecosystem.

>>>>

The combustion community has not yet widely adopted a standard format for
experimental data, but some researchers and groups have proposed solutions to
this problem. Most notably, Frenklach developed the PrIMe (\textbf{Pr}ocess
\textbf{I}nformatics \textbf{M}od\textbf{e}l) data
format~\autocite{Frenklach:2007bm,You:2011hy} and an associated online database,
the PrIMe Data Warehouse (available at \url{http://primekinetics.org}).
PrIMe files encode fundamental
combustion experimental data, along with kinetic models and calculated
quantities, using the eXtensible Markup Language (XML) standard.

PrIMe~\autocite{Frenklach:2007bm,You:2011hy}
has a number of features that make
it a strong standardization format, but it suffers from several flaws that
prevent wide adoption. First, the PrIMe standard does not require or support all
the information needed to simulate an experiment, including a machine-readable
definition of ignition or a standard way to express detailed facility-specific
effects necessary to properly simulate certain experiments. Second, PrIMe uses
internal identifiers for bibliographic references and
species\slash reactions, rather than standard identifiers (e.g., DOIs for
scholarly products, InCHI or SMILES for species). This limits the usability of PrIMe files outside
the PrIMe ecosystem.
